---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fxconvert

<!-- badges: start -->
<!-- badges: end -->

Convert currencies based on rates obtained directly from central banks in an
open and transparent way, without any API dependencies or registration
requirements. Conversion with `fx_convert()` is fully vectorized in amounts,
currencies, and dates, uses local data when available, and downloads up-to-date
rates from a GitHub repository in `parquet` format when needed.
    
## Installation

You can install the development version of `fxconvert` like so:

``` r
pak::pak("torfason/fxconvert")
```

## Example

The package includes a helper function to fill internal gaps in a vector but not
any gaps at the beginning or the end of the vector:

```{r example}
library(fxconvert)
fx_vec_fill_gaps(c(NA, 1, NA, 2, NA))
```

