---
output: github_document
editor_options: 
  chunk_output_type: console
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# fxconvert

<!-- badges: start -->
<!-- badges: end -->

Convert currencies based on rates obtained directly from central banks in an
open and transparent way, without any API dependencies or registration
requirements. Conversion with `fx_convert()` is fully vectorized in amounts,
currencies, and dates, uses local data when available, and downloads up-to-date
rates from a GitHub repository in `parquet` format when needed.
    
## Installation

You can install the development version of `fxconvert` like so:

``` r
pak::pak("torfason/fxconvert")
```

## Examples

Use `fx_get()` to quickly get exchange rates for different currencies and dates,
or use `fx_convert()` to convert amounts directly between currencies based on
the exchange rates on particular dates.

```{r example}
# Load the package
library(fxconvert)

# Initialize the local data store, downloading fx data from GitHub
fx_init(verbose = FALSE)

# Retrieve specific exchange rates on specific dates
fx_get("usd", "eur", "2020-01-03")

# The functions are fully vectorized
fx_get(from   = c("usd", "eur", "gbp"),
       to     = c("eur", "gbp", "usd"),
       fxdate = "2020-01-03") 

# Load dplyr for demonstrating use within a tibble manipulation pipe
library(dplyr, include.only = c("tibble", "mutate"))

# Use fx_convert() to convert amounts between currencies directly
# This is useful when manipulating data frames
d <- tibble(date = c("2020-01-03", "2024-05-06"), 
            price_usd = c(999, 13.7))
d |> 
  mutate(price_eur = fx_convert(price_usd, "usd", "eur", date))
```

## Vectorization and recycling

Both functions are fully vectorized in terms of the following parameters:

- `from` (The currency to convert from)
- `to` (The currency to convert to)
- `fxdate` (The date for the exchange rate to use)

The `fx_convert()` function is also vectorized in terms of the amount:

- `amount` (The amount to convert between currencies)

Recycling follows the tidy recycling rules.
